\subsection{Special Linear Group 3$\times$3}
\label{sec:matsl3}
The Special Linear Group SL(3) is defined by the set of 3$\times$3 matrices $\bf{H}$ that verify the following constraint:
\[
\det(\bf{H}) = 1
\] 

\subsubsection{The object {\tt Rox\_MatSL3}}
\label{sss:matsl3_object}
~\\~\\
A \lstinline$Rox_MatSL3$ object can be declared using the pointer to a \lstinline$Rox_MatSL3_Struct$: 

\begin{lstlisting}
typedef struct Rox_MatSL3_Struct* Rox_MatSL3;
\end{lstlisting}

The structure is opaque to the user and can only be accessed through constructors, destructors and methods described in the following sections.

\subsubsection{Creating/Deleting a {\tt Rox\_MatSL3}}
\label{sss:matsl3_delnew}
~\\~\\
Functions are provided to allocate, initialize and deallocate an \lstinline$Rox_MatSL3$ object~:
\begin{lstlisting}
Rox_Error rox_matsl3_new(Rox_MatSL3 * H);
\end{lstlisting}
The \lstinline$rox_matsl3_new$ function allocates memory for data. By default, the matrix is initialized to the identity.\\ 

% \begin{lstlisting}
% Rox_Matrix rox_matsl3_new_init(const Rox_Real data[9]);
% \end{lstlisting}
% The \lstinline$rox_matsl3_new_init$ function first allocates memory with the default constructor and then copies the parameter `data' to initialize matrix.
% The data contains the entries of the matrix row by row.\\

\begin{lstlisting}
Rox_Error rox_matsl3_del(Rox_MatSL3 * H);
\end{lstlisting}
The \lstinline$rox_matsl3_del$ function deallocates memory for an \lstinline$Rox_MatSL3$ structure. It is necessary to call this function when the
structure is not used any more or before overwriting it.

\subsubsection{Main functions related to {\tt Rox\_MatSL3}}
\label{sss:matsl3_methods}
~\\~\\

Firstly, it is possible to get / set information from \lstinline$Rox_MatSL3$ structure:
\begin{description}
  \item[rox\_matsl3\_get\_data]~: Get a copy of the data of the matsl3 matrix.
%  \item[rox\_matsl3\_get\_value]~: Returns a value of the matsl3 matrix.
  \item[rox\_matsl3\_set\_data]~: Set the data of the matsl3 matrix.
  \item[rox\_matsl3\_set\_value]~: changes a value of the matrix.
\end{description}

Several functions are provided to use matrices, here the most important functions will be described to make basic matrix calculus.
\begin{description}
  \item[rox\_matsl3\_mulmatmat]~: Computes the multiplication of two matrices.
  \item[rox\_matsl3\_inv]~: Computes the inverse of the matrix.
  \item[rox\_matsl3\_display]~: Display the matrix.
\end{description}

Other functions are provided, further information is available in the programmer manual.
