\chapter{Introduction}
\label{cha:intro}

\rox{} is a computer vision software written in strict ANSI-C
and optimized for real-time applications. The optimization has been performed with SSE 4.2 for x86 processors and Neon for Arm processors.
No extra dependencies are required to compile the software, just the standard C library. The software provides advanced
algorithms that can be used for applications like vision-guided robot
control and augmented reality. \\

Contrarily to standard computer vision software, \rox{} uses {\bf
direct methods} and {\bf dense information} to solve computer vision
problems. This approach is more robust and accurate than sparse
features-based methods, but generally requires high computation
resources. The use of a new fast optimization technique called {\bf
ESM (Efficient Second-order Approximation Method)} allows to use dense
direct methods in real-time. The ESM technique was proved to have a
higher convergence rate (third-order) than the Newton optimization
technique (second-order) while being more efficient.\\

The present version of the \rox{} is composed of the following modules~:

\begin{description}
  \item[Utils]~: module with basic structures and functions used by all the other modules ;
  \item[Maths]~: module with mathematical structures and methods ;
  \item[Model]~: module with structures and functions to handle target models ;
  \item[Vision]~: module with structures and functions for computer vision ;
  \item[Detection]~: module with structures and functions for motion detection ;
  \item[Tracking]~: module with structures and methods for visual tracking computation. The output of the module is a homography matrix relative to a target model ;
\end{description}

\input{intro/install.tex}
%\input{intro/coding.tex}
